Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-11-25 rnni_convexity.tex
last para of findpath

Because the algorithm returns a path between pairs of trees in $\rnni$, the length of the path approximates the $\rnni$ distance from above.
A natural question then is how accurate this approximation is.
To answer this question for small trees, we have implemented the algorithm $\findpath$
\todo{LC: github - link}
\autocite{}
and compared the results with the true distance found using the algorithm from Section~\ref{section:algorithms}.
By doing this we could show that $\findpath$ computes correct distances for all trees on up to six taxa.

>>>>

Because the algorithm returns a path between pairs of trees in $\rnni$, the length of the path approximates the $\rnni$ distance from above.
A natural question then is how accurate this approximation is.
We have computationally shown that the algorithm $\findpath$ finds the correct distance for trees up to six taxa.
Specifically, we have implemented $\findpath$
\todo{LC: github - link}
\autocite{}
and compared the results with the true $\rnni$ distance as explained earlier in this section.
